### 2015-12-11 paper/3-features.tex
Update class diagram with more information about overridden methods.
Added explanation of class diagram

>>>>

An overview of this design is given in Figure~\ref{fig:class_diagram}.
It shows that there is a simulation \texttt{Core}, which has several \texttt{AtomicModels} connected to it.
The default \texttt{Core} is merely the sequential simulation core.
Its subclasses define specific variants of the simulation algorithm, like \texttt{ConservativeCore} (conservative synchronization), \texttt{OptimisticCore} (optimistic synchronization), and \texttt{DynamicCore} (\textsf{Dynamic Structure DEVS}).

\begin{figure}
    \includegraphics[width=\columnwidth]{fig/cores_class_diagram.eps}
	\caption{Dxex kernel design.}
	\label{fig:class_diagram}
\end{figure}
